Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-15 Publications/2013-IPMI/Latex/00-Main.tex
Merged Dominique's and mine commits.
New Abstract (v.3.0)
Add llncs template. Close #43

\documentclass{llncs}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{acronym}
\usepackage[numbers]{natbib}
\bibliographystyle{splncs03} 
%\bibliographystyle{splncsnat} 
%\bibliographystyle{IEEEtran}

\usepackage[hyphens]{url}
\usepackage{nameref}
\usepackage[breaklinks]{hyperref}
\usepackage[USenglish]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pslatex}
%

\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\argmax}{argmax}
\DeclareMathOperator{\argmin}{argmin}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\dist}{dist}
\DeclareMathOperator{\const}{Const.}

\usepackage{graphicx}

%
%\tableofcontents
%
\mainmatter              % start of the contributions
%
\graphicspath{{../Figures/}}

@@

\title{Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors}
%%
\titlerunning{Segmentation & EPI correction on DWI}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Oscar Esteban\inst{1,2} \and
        Alessandro Daducci \inst{2} \and
		Meritxell Bach-Cuadra \inst{2,4} \and
		Mar\'ia-Jes\'us Ledesma-Carbayo \inst{1} \and 
        Jean-Philippe Thiran \inst{2,4} \and
        Andr\'es Santos \inst{1} \and
        Dominique Zosso \inst{3,2}}
%
\authorrunning{Oscar Esteban et al.} % abbreviated author list (for running head)

@@

\input{02-Abstract}

@@

>>>>

\documentclass{llncs}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{acronym}
\usepackage[numbers]{natbib}
\bibliographystyle{splncs03}

\usepackage{nameref}
\usepackage{hyperref}
\usepackage[hyphens]{url}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[USenglish]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pslatex}
%
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\argmax}{argmax}
\DeclareMathOperator{\argmin}{argmin}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\dist}{dist}
\DeclareMathOperator{\const}{Const.}

\usepackage{graphicx}
%
%\tableofcontents
%
\mainmatter              % start of the contributions
%
\graphicspath{{../Figures/}}

@@

\title{Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors}
%%
\titlerunning{Segmentation & EPI correction on DWI}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Oscar Esteban\inst{1,2} \and
        Alessandro Daducci \inst{2} \and
		Meritxell Bach-Cuadra \inst{2,4} \and
        Jean-Philippe Thiran \inst{2,4} \and
        Andr\'es Santos \inst{1} \and
        Dominique Zosso \inst{3,2}}
%
\authorrunning{Oscar Esteban et al.} % abbreviated author list (for running head)

@@

\begin{abstract}
\input{02-Abstract}
\keywords{ diffusion weighted imaging, connectomics,
           echo planar imaging, magnetic resonance, 
           segmentation, registration, distortion correction}
\end{abstract}

@@

%\input{07-Acknowledgments}

### 2012-12-15 Publications/2013-IPMI/Latex/02-Abstract.tex
Add llncs template. Close #43

Whole-brain connectivity analysis on diffusion weighted MR images (DWI) involves
a large set of processing techniques. Particularly, an accurate white matter (WM)
segmentation is required, with precise location of the interface with grey matter.
High-standard segmentation and surface parcellations are readily available on 
anatomical images, such as T1-weighted MRI. However DWI typically have drastically 
lower resolution, and generally exhibit important distortions. Here, we propose a 
segmentation-registration framework that exploits the detailed anatomy extracted 
from anatomical MRI as reference shape-prior for DWI segmentation. We use the 
active contours without edges model to look for a deformation field that optimally 
maps the shape prior on the multivariate features in diffusion space. This joint
approach attends the intrinsic coupling of segmentation, parcellation, and distortion 
correction problems to finally obtain reliable connectivity networks. Preliminary
results on synthetic datasets and simulated DWI confirm the effectiveness of our 
approach.

>>>>

In whole-brain connectivity analysis of diffusion weighted MR images (DWI),
an accurate delineation of the white-matter and grey-matter surfaces is required.
While high-standard segmentation is readily available for anatomical MRI, such 
as T1-weighted, DWI typically have drastically lower resolution and strong 
geometrical distortions. We propose a DWI segmentation-registration framework 
that exploits the detailed anatomy extracted from anatomical MRI as shape-prior.
We use an ``active contours without edges''-like model to look for a deformation
field that optimally maps the shape prior on the multivariate features 
in diffusion space. This joint approach reflects the intrinsic coupling of 
segmentation and distortion correction. Complementary, a precise and consistent
cortical parcellation on DWI is straightforward by projection from T1 space. Thus,
we expect to improve the reliability and robustness of the resulting connectivity 
networks and their comparability within and across subjects. Preliminary results 
on synthetic datasets and simulated DWI confirm the effectiveness of our approach.
